\plaintitle

### 2017-06-05 papers/IoT2017/analysis.tex
no message

\subsection{Privacy}

Due to the communication anonymity and mixing services, members of a microgrid can see only the amount of energy and financial assets withdrawn by a prosumer.
Since all trading transactions are anonymous, the amount of assets traded by the prosumer will not be publicly known.
In case a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
Note that even if a prosumer does not wish to trade, it should always withdraw and mix assets; otherwise, the lack of withdrawal would leak information.

As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
\Aron{Also knows financial amounts, but those are necessary for billing.}
Since trading is anonymous, it does not receive any further information.

In fact, we can provide an even higher-level of privacy.
Since price policies are recorded on the ledger, which the smart meters may read, the smart meters can calculate the prosumer's monthly bill, and send only this single financial amount to the DSO each month.
Meanwhile, the DSO can still obtain current and future load information from the bid storage and from the trades recorded on the ledger.

>>>>

\subsection{Privacy}
Due to the use of communication anonymity and mixing services, members of a microgrid can observe only the amount of assets withdrawn by a prosumer from its smart meter. % the amount of energy and financial assets withdrawn by a prosumer.
Since all trading transactions are anonymous, they do not reveal the actual amount of assets traded by the prosumer.
If a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
Note that even if a prosumer does not wish to trade, it should always withdraw, mix, and deposit the same amount of assets.
Otherwise, the lack (or varying amount) of withdrawal would leak information.

As for the DSO, it receives the same information from the smart meter as in a non-transactive smart grid (i.e., amount of energy produced and consumed).
Since trading is anonymous, the DSO learns only the financial balance of the prosumer, which is necessary for billing.

However, we can provide an even higher-level of privacy.
Since price policies are recorded on the ledger, which the smart meters may read, each prosumer's smart meter may calculate and send the prosumer's monthly bill to the DSO, without revealing the prosumer's energy consumption or production.
Meanwhile, the DSO can still obtain very detailed load information (including predictions) for the microgrid from the bid storage and the trades recorded on the ledger.
